Centers and centralizers of higher enveloping algebras of Lie algebras

### 2020-09-09 draft.tex
small tweaks

\greg{We could relate this to $P_n$-center of $\fg$. That shall also (but I have to think about the proof more), 
at least up to formality gives the $P_{n+1}$-structure on it. }\owen{Brian now does this in the TFT section.}

@@

For a reductive Lie algebra $\fg$, the Harish-Chandra isomorphism is an isomorphism of commutative algebras
\[
Z(U(\fg)) \xto{\cong} {\rm Sym} (\fh)^W
\]
where $\fh$ is a Cartan subalgebra and $W$ is the Weyl group of $\fg$. 
Here $Z(U(\fg))$ denotes the ordinary center of the associative algebra $U(\fg)$.

The following result generalizes (and implies) the Harish--Chandra isomorphism for the $\EE_n$-center of the $\EE_n$-enveloping algebra.

@@

@@

\begin{rmk}
One way to formulate the definition of a $\PP_{[n+1,n]}$ algebra $(A,B)$ is to require a map of commutative dg algebras $A \to B$ together with a lift to a map of $\PP_{n+1}$ algebras $A \to \fZ_{\PP_n} (B)$, where $\fZ_{\PP_n}(B)$ is the {\em $\PP_n$-center} of the $\PP_n$ algebra $B$. 
By a similar proof as in the main part of the paper, we expect that one can see that the factorization algebra
\[
\clies \bigg(\Omega^\bu \otimes \fg \; ; \; {\rm Sym} \left(\Omega^\bu_c \otimes \fg [1] \right) \bigg)
\]
is a model for the $\PP_n$-center of the $\PP_n$-{\em enveloping algebra} $\UU_{\PP_n} (\fg) = {\rm Sym} (\fg [1-n])$. 
\end{rmk}

@@

\begin{dfn}
\label{dfn:constructible1}
Let $\bC_n(\fg)$ be the following constructible factorization algebra on $M \times \RR_{\geq 0}$:
\begin{itemize}
\item to an open set $U \subset M \times \RR_{> 0}$, we assign the cochain complex 
\[
\bC_n (\fg) (U) = \clies \bigg(\fg \otimes \Omega^\bu (U) \; , \; \Sym \left(\fg \otimes \Omega^\bu_c(U) [2] \right) \bigg) .
\]
\item to an open set $V \times [0,\epsilon)$ we assign the cochain complex 
\[
\bC_n (\fg) (V \times [0,\epsilon)) = \clies\bigg(\fg \otimes \Omega^\bu(V) \Hat{\otimes} \Tilde{\Omega}^\bu([0,\epsilon))  \; , \; \Sym\left(\fg \otimes \Omega^\bu_c (V \times [0,\epsilon))[2] \right) \bigg).
\]
%\brian{this is wrong
%\[
%\bC_n (\fg) (V \times [0,\epsilon)) = {\rm Sym} \left(\fg \otimes \Omega^\bu_c (V \times [0,\epsilon) [2] \right).
%\]
%}
\end{itemize}
The structure map associated to the embedding 
\begin{equation}\label{eqn:embed}
i : U \sqcup V \times [0, \epsilon) \hookrightarrow V' \times [0,\epsilon')
\end{equation}
is given by the composition
\[
\begin{tikzcd}
\clies \bigg(\fg \otimes \Omega^\bu (U) \; , \; \Sym \left(\fg \otimes \Omega^\bu_c(U) [2] \right) \bigg) \; \otimes \;  \clies\bigg(\fg \otimes \Omega^\bu(V) \otimes \Tilde{\Omega}^\bu([0,\epsilon))  \; , \; \Sym\left(\fg \otimes \Omega^\bu_c (V \times [0,\epsilon))[2] \right) \bigg) \ar[d, "\simeq"] \\
\clies \bigg(\fg \otimes \left(\Omega^\bu (U) \oplus \Omega^\bu(V) \Hat{\otimes} \Tilde{\Omega}^\bu([0,\epsilon)) \right) \; , \; \Sym \left(\fg \otimes \left(\Omega^\bu_c(U) [2] \oplus \Omega^\bu_c(V \times [0,\epsilon)) [2]\right)\right) \bigg) \ar[d, "i^* \otimes i_*"] \\
\clies\bigg(\fg \otimes \Omega^\bu(V') \Hat{\otimes} \Tilde{\Omega}^\bu([0,\epsilon'))  \; , \; \Sym\left(\fg \otimes \Omega^\bu_c (V' \times [0,\epsilon'))[2] \right) \bigg).
\end{tikzcd}
\]

%\Sym \left(\fg \otimes \Omega^\bu_c(U) [2] \right) \; \otimes \; \Sym \left(\fg \otimes \Omega^\bu_c (V \times [0,\epsilon)) [2] \right) \ar[d, "\simeq"] \\
%\Sym\left(\fg \otimes \left(\Omega^\bu_c(U) \oplus \Omega^\bu_c(V \times [0,\epsilon)) \right) [2] \right) \ar[d, "i_*"]\\
%\Sym \left( \fg \otimes \Omega^\bu_c(V' \times [0,\epsilon')) [2] \right)
The first map uses the fact that the symmetric algebra functor is monoidal. 
The second map is induced from restriction and extension of de Rham forms and compactly supported de Rham forms along the embedding (\ref{eqn:embed}). 
\end{dfn}

\begin{rmk}
Here, we remark that pulling back along an embedding $\iota : U \hookrightarrow V \times [0,\epsilon)$, where $U \subset M \times \RR_{>0}$ determines a composition of cochain complexes
\[
\Omega^\bu (V') \otimes \Tilde{\Omega}^\bu([0,\epsilon)) \xto{j^*}  \Omega^\bu (V') \Hat{\otimes} \Omega^\bu((0,\epsilon)) \cong \Omega^\bu(V \times (0,\epsilon)) \xto{\iota^*} \Omega^\bu(U) .
\]
This is our model for restriction $\iota^*$ of de Rham forms that is used in the definition above.
\end{rmk}

On each open set $U \subset M \times \RR_{\geq 0}$, the cochain complex $\bC_n(\fg) (U)$ is a commutative dg algebra. 
In fact, it has the structure of a $\PP_0$ algebra where the $1$-shifted bracket $\{\cdot, \cdot\}$ is defined as follows.

\begin{lmm}
$\bC_n(\fg)$ admits the structure of a constructible $\PP_0$-factorization algebra on~$M \times \RR_{\geq 0}$. 
\end{lmm}

@@

For any Lie group $G$, there is a gauge theory defined in any dimension known as {\em topological BF theory}.
Let the ``spacetime'' be an $(n+1)$-dimensional manifold $N$, 
which for now we assume has no boundary $\partial N = \emptyset$. 
As a field theory, there is a system of PDE known as the ``solutions to the equations of motion.''
When $N$ is compact, the moduli space of solutions to these equations of motion for topological BF theory can be described as the mapping space 
\begin{equation} 
\label{stack1}
{\rm Map}(N_{\rm dR} ,  {\rm T}^*[n] {\rm B} G),
\end{equation}
where $N_{\rm dR}$ denotes the de Rham stack of $N$ and where ${\rm B}G$ is the classifying stack of $G$.
Via the canonical $n$-shifted symplectic structure on ${\rm T}^* [n] {\rm B} G$, 
the AKSZ construction equips this mapping space with a $(-1)$-shifted symplectic structure. 
On manifolds without boundary, this procedure describes topological BF theory in the Batalin--Vilkovisky formalism~\cite{BV}.

@@

It is the central theme of \cite{CG1, CG2} that the observables of a {\em perturbative} field theory define the structure of a factorization algebra. 
Moreover, the observables are equipped with the structure of a $\PP_0$-factorization algebra.

@@

\begin{rmk}
The $L_\infty$ algebra $\cL$ in (\ref{eqn:fields}) can be enhanced to a sheaf of $L_\infty$ algebras,
and it can be understood as a generalized topological BF theory. 
In the setup of \cite{CG2}, the factorization algebra of classical observables of generalized topological BF theory is given by the Chevalley--Eilenberg cochains $\clies (\cL)$.   
The $\PP_0$-structure is induced from the explicit $(-1)$-symplectic pairing $\int A \wedge B$ at the level of the fields. 
\end{rmk}

>>>>

\greg{We could relate this to $P_n$ center of $\fg$. That shall also (but I have to think about the proof more), 
at least up to formality gives the $P_{n+1}$ structure on it. }\owen{Brian now does this in the TFT section.}

@@

For a reductive Lie group $G$, the Harish-Chandra isomorphism is an isomorphism of commutative algebras
\[
Z(U(\fg)) \xto{\cong} {\rm Sym} (\fh)^W,
\]
where $\fh$ is a Cartan subalgebra of the Lie algebra $\fg$ of $G$ and $W$ is the Weyl group of $G$. 
Here $Z(U(\fg))$ denotes the ordinary center of the associative algebra~$U(\fg)$.

The following result generalizes the Harish--Chandra isomorphism to the $\EE_n$ center of the  enveloping $\EE_n$ algebra.

@@

\owen{I think the usual Chevalley theorem only applies when $1-n$ is an even integer. I'm not sure what the theorem is called when $1-n$ is odd.}

@@

\begin{rmk}
One way to formulate the definition of a $\PP_{[n+1,n]}$ algebra $(A,B)$ is to require a map of commutative dg algebras $A \to B$ together with a lift to a map of $\PP_{n+1}$ algebras $A \to \fZ_{\PP_n} (B)$, where $\fZ_{\PP_n}(B)$ is the {\em $\PP_n$ center} of the $\PP_n$ algebra $B$. 
By a similar proof as in the main part of the paper, we expect that one can see that the factorization algebra
\[
\clies \bigg(\Omega^\bu \otimes \fg \; ; \; {\rm Sym} \left(\Omega^\bu_c \otimes \fg [1] \right) \bigg)
\]
is a model for the $\PP_n$ center of the {\em enveloping $\PP_n$ algebra} $\UU_{\PP_n} (\fg) = {\rm Sym} (\fg [1-n])$. 
\end{rmk}

@@

\begin{dfn}
\label{dfn:constructible1}
Let $\bC_n(\fg)$ be the following constructible factorization algebra on $M \times \RR_{\geq 0}$:
\begin{itemize}
\item to an open set $U \subset M \times \RR_{> 0}$, we assign the cochain complex 
\[
\bC_n (\fg) (U) = \clies \bigg(\fg \otimes \Omega^\bu (U) \; , \; \Sym \left(\fg \otimes \Omega^\bu_c(U) [2] \right) \bigg) .
\]
\item to an open set $V \times [0,\epsilon)$ we assign the cochain complex 
\[
\bC_n (\fg) (V \times [0,\epsilon)) = \clies\bigg(\fg \otimes \Omega^\bu(V) \Hat{\otimes} \Tilde{\Omega}^\bu([0,\epsilon))  \; , \; \Sym\left(\fg \otimes \Omega^\bu_c (V \times [0,\epsilon))[2] \right) \bigg).
\]
%\brian{this is wrong
%\[
%\bC_n (\fg) (V \times [0,\epsilon)) = {\rm Sym} \left(\fg \otimes \Omega^\bu_c (V \times [0,\epsilon) [2] \right).
%\]
%}
\end{itemize}
The structure map associated to the embedding 
\begin{equation}\label{eqn:embed}
i : U \sqcup V \times [0, \epsilon) \hookrightarrow V' \times [0,\epsilon')
\end{equation}
is given by the composition
\[
\begin{tikzcd}
\clies \bigg(\fg \otimes \Omega^\bu (U) \; , \; \Sym \left(\fg \otimes \Omega^\bu_c(U) [2] \right) \bigg) \; \otimes \;  \clies\bigg(\fg \otimes \Omega^\bu(V) \otimes \Tilde{\Omega}^\bu([0,\epsilon))  \; , \; \Sym\left(\fg \otimes \Omega^\bu_c (V \times [0,\epsilon))[2] \right) \bigg) \ar[d, "\simeq"] \\
\clies \bigg(\fg \otimes \left(\Omega^\bu (U) \oplus \Omega^\bu(V) \Hat{\otimes} \Tilde{\Omega}^\bu([0,\epsilon)) \right) \; , \; \Sym \left(\fg \otimes \left(\Omega^\bu_c(U) [2] \oplus \Omega^\bu_c(V \times [0,\epsilon)) [2]\right)\right) \bigg) \ar[d, "i^* \otimes i_*"] \\
\clies\bigg(\fg \otimes \Omega^\bu(V') \Hat{\otimes} \Tilde{\Omega}^\bu([0,\epsilon'))  \; , \; \Sym\left(\fg \otimes \Omega^\bu_c (V' \times [0,\epsilon'))[2] \right) \bigg).
\end{tikzcd}
\]
%\Sym \left(\fg \otimes \Omega^\bu_c(U) [2] \right) \; \otimes \; \Sym \left(\fg \otimes \Omega^\bu_c (V \times [0,\epsilon)) [2] \right) \ar[d, "\simeq"] \\
%\Sym\left(\fg \otimes \left(\Omega^\bu_c(U) \oplus \Omega^\bu_c(V \times [0,\epsilon)) \right) [2] \right) \ar[d, "i_*"]\\
%\Sym \left( \fg \otimes \Omega^\bu_c(V' \times [0,\epsilon')) [2] \right)
The first map uses the fact that the symmetric algebra functor is monoidal. 
The second map is induced from restriction and extension of de Rham forms and compactly supported de Rham forms along the embedding (\ref{eqn:embed}). 
\end{dfn}

\begin{rmk}
For an open $U \subset M \times \RR_{>0}$, pulling back along an embedding $\iota : U \hookrightarrow V \times [0,\epsilon)$ determines a composition of cochain complexes
\[
\Omega^\bu (V') \otimes \Tilde{\Omega}^\bu([0,\epsilon)) \xto{j^*}  \Omega^\bu (V') \Hat{\otimes} \Omega^\bu((0,\epsilon)) \cong \Omega^\bu(V \times (0,\epsilon)) \xto{\iota^*} \Omega^\bu(U) .
\]
This is our model for restriction $\iota^*$ of de Rham forms that is used in the definition above.
\end{rmk}

On each open set $U \subset M \times \RR_{\geq 0}$, the cochain complex $\bC_n(\fg) (U)$ is a dg commutative algebra. 
In fact, it has the structure of a $\PP_0$ algebra where the $1$-shifted bracket $\{\cdot, \cdot\}$ is defined as follows.

\begin{lmm}
$\bC_n(\fg)$ admits the structure of a constructible $\PP_0$ factorization algebra on~$M \times \RR_{\geq 0}$. 
\end{lmm}

@@

For any Lie group $G$, there is a gauge theory defined in any dimension known as {\em topological BF theory}.
Let the ``spacetime'' be an $(n+1)$-dimensional manifold $N$, 
which for now we assume has no boundary $\partial N = \emptyset$. 
For a field theory, there is a system of PDE, known as the equations of motion, that govern the behavior of the system.
When $N$ is compact, the moduli space of ``solutions to the equations of motion'' for topological BF theory is provided the mapping space 
\begin{equation} 
\label{stack1}
{\rm Map}(N_{\rm dR} ,  {\rm T}^*[n] {\rm B} G),
\end{equation}
where $N_{\rm dR}$ denotes the de Rham stack of $N$ and where ${\rm B}G$ is the classifying stack of $G$.
Via the canonical $n$-shifted symplectic structure on ${\rm T}^* [n] {\rm B} G$, 
the AKSZ construction equips this mapping space with a $(-1)$-shifted symplectic structure. 
On manifolds without boundary, this procedure describes topological BF theory in the Batalin--Vilkovisky formalism~\cite{BV}.

@@

It is the central theme of \cite{CG1, CG2} that the observables of a {\em perturbative} field theory define the structure of a factorization algebra. 
Moreover, the observables are equipped with the structure of a $\PP_0$ factorization algebra.

@@

\begin{rmk}
The $L_\infty$ algebra $\cL$ in (\ref{eqn:fields}) can be enhanced to a sheaf of $L_\infty$ algebras,
and it can be understood as a generalized topological BF theory. 
In the setup of \cite{CG2}, the factorization algebra of classical observables of generalized topological BF theory is given by the Chevalley--Eilenberg cochains $\clies (\cL)$.   
The $\PP_0$ structure is induced from the explicit $(-1)$-symplectic pairing $\int A \wedge B$ at the level of the fields. 
\end{rmk}
